\documentclass[12pt, a4paper]{article}

\usepackage[a4paper, margin=1in]{geometry}

\input{preamble}
\input{letterfonts}

\newcommand{\mytitle}{CS2040S Tutorial 8}
\newcommand{\myauthor}{github/omgeta}
\newcommand{\mydate}{AY 24/25 Sem 2}

\begin{document}
\raggedright
\footnotesize
\begin{center}
{\normalsize{\textbf{\mytitle}}} \\
{\footnotesize{\mydate\hspace{2pt}\textemdash\hspace{2pt}\myauthor}}
\end{center}
\setlist{topsep=-1em, itemsep=-1em, parsep=2em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                      Begin                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}[Q\arabic*.]
  \item 
    \begin{enumerate}[(\alph*)]
      \item Since every node is visited at most once, it cannot possibly be visited from a different node from the parent node to form a cycle. 

      \item Same algorithm can be used for both trees and graphs, but running on a non-root in a tree may cause nodes other than the subtree rooted at that non-root to be missed.
    \end{enumerate}

  \item Solution:
    \begin{enumproof}
    \item BFS/DFS on any unvisited node, marking all nodes traversed as visited 
    \item When there are no more nodes, increment count of CC by 1 and repeat step 1
    \end{enumproof}

  \item Solution:
    \begin{enumproof}
    \item BFS on $n$ nodes, tracking edges encountered
    \item Tree iff $n-1$ edges for $n$ nodes
    \end{enumproof}

  \item 
    \begin{enumerate}[(\alph*.)]
      \item 1. Directed graph with nodes as people and edges as spread\\
        2. Special types of edges?

      \item Bipartite graph with people and location edges.

      \item ?

      \item Undirected graph with nodes as students and edges as similarity. Any non-trivial components are cheaters.

      \item Bipartite graph with children and preesent nodes, edges as desire. Greedy allocation with priority given to children with smaller desire.
    \end{enumerate}

  \item 
    \begin{enumerate}[(\alph*.)]
      \item 

      \item DFS, because resolving each letter first would give us more info for later letters.

      \item Search finishes when there is only 1 edge.
    \end{enumerate}

  \item Bipartite graph with nodes as students and edges between nodes if students are on the same card.\\
    Consistency: check bipartitite with BFS/DFS in a way that $|G| > |B|$\\
    Sufficiency: Insufficient if no possible permutations of flipping $G, B$ for connected components leads to a consistent solution.\\
    Assuming both consistent and sufficient, assign in a way that for each connected component, we prioritise $|G| > |B|$

  \item ?
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                       End                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
