\documentclass[12pt, a4paper]{article}

\usepackage[a4paper, margin=1in]{geometry}

\input{preamble}
\input{letterfonts}

\newcommand{\mytitle}{CS2040S Tutorial 5}
\newcommand{\myauthor}{github/omgeta}
\newcommand{\mydate}{AY 24/25 Sem 2}

\begin{document}
\raggedright
\footnotesize
\begin{center}
{\normalsize{\textbf{\mytitle}}} \\
{\footnotesize{\mydate\hspace{2pt}\textemdash\hspace{2pt}\myauthor}}
\end{center}
\setlist{topsep=-1em, itemsep=-1em, parsep=2em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                      Begin                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}[Q\arabic*.]
  \item Time complexity of operations on AVL is $O(L \log N)$ vs $O(L)$ for trie. Space complexity for both is $O(L)$ but tries have more overhead cost.

  \item 
    \begin{enumerate}[(\alph*.)]
      \item For each subtree, there is a horizontal or vertical split. For a horizontal split, check $x$ to split value and go left or right. Vice versa for vertical split on $y$ coord, going up or down. Time complexity: $O(h)$

      \item Use QuickSelect to select median at each level and partition. Time complexity: $O(n\log n)$

      \item At horizontal split, recurse on left child. At vertical split, recurse on both children. Time complexity: $O(\sqrt{n})$
    \end{enumerate}

  \item In a Trie, store a count of names under the node, for each gender. On insertion, update counts at the nodes. \lstinline|countPrefix|: return count stored at node. \lstinline|countName|: search for node and if end of word, return count of node $-$ count of child nodes. \lstinline|countBetween|: Find begin and end node ranks, then return $endRank - beginRank - countName(begin)$

  \item 
    \begin{enumerate}[(\alph*.)]
      \item Using a Trie storing bits, insert numbers from MSB to LSB. To find the best best value of $y$ to XOR with $x$: if the current bit is $0$, go down bit $1$ if it exists else $0$.
    \end{enumerate}
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                       End                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
